---
title: "Report 3 - Mothers' contingent talks"
date: "13/08/2018"
output:
  pdf_document:
    fig_height: 3.5
    fig_width: 5
    number_sections: yes
fontsize: 11pt
params:
  version: "v3.0"
  version-date: "13/08/2018"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.align = "center")
knitr::opts_knit$set(root.dir = normalizePath("../../"))
library(tidyverse)
theme_set(theme_minimal())
scale_colour_discrete <- function(...) scale_color_brewer(..., type = "qual", palette = "Dark2")
scale_fill_discrete <- function(...) scale_fill_brewer(..., type = "qual", palette = "Dark2")
```

```{r read-data, message=FALSE}
gestures <- read_csv("./data/gestures.csv")

gestures_tot <- gestures %>%
  group_by(dyad, background, months, gesture) %>%
  summarise(
    count = sum(count),
    ct = sum(ct)
  ) %>%
  ungroup() %>%
  mutate(
    gesture = factor(gesture, levels = c("reach", "point", "ho_gv"))
  ) %>%
  mutate_if(is.character, as.factor)
```

For information on the data set, see Report 2.

The following histogram shows counts of the mothers' contingent talks by gesture type. There are a lot of 0s in all gestures.

```{r ct-hist, warning=FALSE}
gestures_tot %>%
  ggplot(aes(ct, fill = gesture)) +
  geom_histogram(binwidth = 3) +
  facet_grid(~ gesture) +
  labs(
    title = "Number of mothers' contingent talks by gesture type",
    x = "Contingent talks"
  )
```

The situation is quite similar across cultural backgrounds. There is an appreaciable outlier mother in the point English data: she is the mother of the 'super pointer' (E05).

```{r ct-hist-2, warning=FALSE}
gestures_tot %>%
  ggplot(aes(ct, fill = background)) +
  geom_histogram(binwidth = 3) +
  facet_grid(background ~ gesture) +
  labs(
    title = "Number of contingent talks by gesture and background",
    x = "Contingent talks"
  )
```

The medians in the stripchart below do not show a visible increase of contingent talks over time.

```{r ct-jitt-med}
gestures_tot %>%
  filter(ct < 20) %>%
  ggplot(aes(as.factor(months), ct)) +
  geom_jitter(width = 0.2, alpha = 0.3) +
  stat_summary(fun.y = median, geom = "point", shape = 18, size = 5, color = "red") +
  labs(
    title = "Stripchart of contingent talk counts over visit time",
    subtitle = "The red diamonds are medians",
    caption = "Excluding E05",
    x = "Visit time (child's months)",
    y = "Contingent talks (count)"
  )
```

Although the mean instead shows a count increase (it is not surprising that the mean and not the meadian shows the increase, given the high number of 0s in the data).

```{r ct-jitt-mean}
gestures_tot %>%
  filter(ct < 20) %>%
  ggplot(aes(as.factor(months), ct)) +
  geom_jitter(width = 0.2, alpha = 0.3) +
  stat_summary(fun.y = mean, geom = "point", shape = 18, size = 5, color = "red") +
  labs(
    title = "Stripchart of contingent talk counts over visit time",
    subtitle = "The red diamonds are means",
    caption = "Excluding E05",
    x = "Visit time (child's months)",
    y = "Contingent talks (count)"
  )
```

Indeed, there are mothers that increase the number of contingent talks through visit time, especially in releation to the child's points and HGs.

```{r ct-connect}
gestures_tot %>%
  filter(ct < 20) %>%
  ggplot(aes(as.factor(months), ct, group = dyad, colour = gesture)) +
  geom_point() +
  geom_line(alpha = 0.2) +
  facet_grid(~ gesture) +
  labs(
    title = "Contingent talk counts over visit time by gesture type",
    caption = "Excluding E05",
    x = "Visit time (child's months)",
    y = "Contingent talks (count)"
  )
```

The mothers with increasing CTs are mostly Chinese and English.

```{r ct-connect-background, fig.dim = c(7, 6)}
gestures_tot %>%
  filter(ct < 20) %>%
  ggplot(aes(as.factor(months), ct, group = dyad, colour = background)) +
  geom_point() +
  geom_line(alpha = 0.2) +
  facet_grid(background ~ gesture) +
  labs(
    title = "Contingent talk counts over visit time by gesture type and background",
    caption = "Excluding E05",
    x = "Visit time (child's months)",
    y = "Contingent talks (count)"
  ) +
  theme(legend.position = "top")
```
