---
title: "Report 8"
date: "07/01/2019"
output:
  pdf_document:
    fig_height: 4
    fig_width: 5
    highlight: tango
    number_sections: yes
fontsize: 11pt
params:
  version: "v2.0"
  version-date: "07/01/2019"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = normalizePath("../../"))
library(fitdistrplus)
library(tidyverse)
theme_set(theme_minimal())
library(lmerTest)
library(sjPlot)
```

```{r read, message=FALSE, warning=FALSE}
gestures <- read_csv("./data/gestures.csv")

gestures_tot <- gestures %>%
  group_by(dyad, background, months, gesture) %>%
  summarise(
    count = sum(count),
    ct = sum(ct)
  ) %>%
  ungroup() %>%
  mutate(
    gesture = factor(gesture, levels = c("reach", "point", "ho_gv"))
  ) %>%
  mutate_if(is.character, as.factor)

utterances <- read_csv("./data/utterances.csv")

# NAs not removed in sum()
utterances_tot <- utterances %>%
  group_by(dyad, background, months) %>%
  summarise(
    utterances = sum(utterances)
  ) %>%
  ungroup() %>%
  mutate_if(is.character, as.factor)

point <- gestures %>%
  filter(gesture == "point") %>%
  group_by(dyad, background, months) %>%
  summarise(
    count = sum(count)
  ) %>%
  ungroup() %>%
  mutate_if(is.character, as.factor)

utter_point <- left_join(utterances_tot, point) %>%
  rename(point = count)

utterances_compl <- utterances %>% na.omit()
utterances_tcompl <- utterances_tot %>% na.omit()

hgp_tot <- gestures_tot %>%
  filter(gesture != "reach") %>%
  group_by(dyad, background) %>%
  summarise(hgp_tot = sum(count))

reach_tot <- gestures_tot %>%
  filter(gesture == "reach") %>%
  group_by(dyad, background) %>%
  summarise(reach_tot = sum(count))

vocab_gest <- gestures_tot %>%
  group_by(dyad, background) %>%
  summarise(count_tot = sum(count), ct_tot = sum(ct)) %>%
  full_join(y = hgp_tot) %>%
  full_join(y = reach_tot)

vocab_utt <- utterances_tot %>%
  group_by(dyad, background) %>%
  summarise(utt_tot = sum(utterances))

vocab <- read_csv("./data/vocab.csv") %>%
  full_join(y = vocab_gest) %>%
  full_join(y = vocab_utt) %>%
  arrange(dyad, months) %>%
  mutate_if(is.character, as.factor)
```

# Summary

Including background and interactions in the model leads to non-significant estimates. This summary is based on models with just the relevant count predictor (all gestures, holdout and gives, utterances, etc) and months, with an interaction between count and months. A by-dyad random intercept has been included in all models.

The estimate of understood and understood/said words is higher at 18 months than at 12 months.

The count of all infant gestures together (HoG, points, reaches) is in a significant interaction with months when the outcome variable is understood/said words: the count of infant gestures is positively correlated with understood/said words at 18 months, but not really at 12 months.
A similar pattern can be seen with the H&G and points count, and the contingent talks count.
The effect of count of maternal utterances and reaches on understood and understood/said word count is not significant.

# All infant gestures

A model with number of understood words as outcome; as predictors: infant gestures count, months, background, all interactions; by-dyad random intercepts.

```{r}
all_gest_lm <- lmer(
  understand ~
    count_tot *
    months *
    background +
    (1|dyad),
  data = vocab
)
summary(all_gest_lm)
```

A model with number of understood words as outcome; as predictors: infant gestures count, months, and interaction between the two; by-dyad random intercepts.

```{r}
all_gest_lm_2 <- lmer(
  understand ~
    count_tot *
    months +
    (1|dyad),
  data = vocab
)
summary(all_gest_lm_2)
```

```{r}
plot_model(all_gest_lm_2, type = "pred", terms = c("count_tot", "months"))
```

A model with number of understood/said words as outcome; as predictors: infant gestures count, months, and interaction between the two; by-dyad random intercepts.

```{r}
all_gest_lm_2_undsay <- lmer(
  und_say ~
    count_tot *
    months +
    (1|dyad),
  data = vocab
)
summary(all_gest_lm_2_undsay)
```

```{r}
plot_model(all_gest_lm_2_undsay, type = "pred", terms = c("count_tot", "months"))
```

# HoGs and points

A model with number of understood words as outcome; as predictors: H&G and points count, months, background and all interaction; by-dyad random intercepts.

```{r}
hgp_lm <- lmer(
  understand ~
    hgp_tot *
    months *
    background +
    (1|dyad),
  data = vocab
)
summary(hgp_lm)
```

A model with number of understood words as outcome; as predictors: H&G and points count, months, and interaction between the two; by-dyad random intercepts.

```{r}
hgp_lm_2 <- lmer(
  understand ~
    hgp_tot *
    months +
    (1|dyad),
  data = vocab
)
summary(hgp_lm_2)
```

```{r}
plot_model(hgp_lm_2, type = "pred", terms = c("hgp_tot", "months"))
```

A model with number of understood/said words as outcome; as predictors: H&G and points count, months, and interaction between the two; by-dyad random intercepts.

```{r}
hgp_lm_2_undsay <- lmer(
  und_say ~
    hgp_tot *
    months +
    (1|dyad),
  data = vocab
)
summary(hgp_lm_2_undsay)
```

```{r}
plot_model(hgp_lm_2_undsay, type = "pred", terms = c("hgp_tot", "months"))
```

# Reaches

A model with number of understood words as outcome; as predictors: reaches count, months, background and all interaction; by-dyad random intercepts.

```{r}
reach_lm <- lmer(
  understand ~
    reach_tot *
    months *
    background +
    (1|dyad),
  data = vocab
)
summary(reach_lm)
```

A model with number of understood words as outcome; as predictors: reaches count, months, and interaction between the two; by-dyad random intercepts.

```{r}
reach_lm_2 <- lmer(
  understand ~
    reach_tot *
    months +
    (1|dyad),
  data = vocab
)
summary(reach_lm_2)
```

```{r}
plot_model(reach_lm_2, type = "pred", terms = c("reach_tot", "months"))
```

A model with number of understood/said words as outcome; as predictors: reach count, months, and interaction between the two; by-dyad random intercepts.

```{r}
reach_lm_2_undsay <- lmer(
  und_say ~
    reach_tot *
    months +
    (1|dyad),
  data = vocab
)
summary(reach_lm_2_undsay)
```

```{r}
plot_model(reach_lm_2_undsay, type = "pred", terms = c("reach_tot", "months"))
```

# Contigent talks

A model with number of understood words as outcome; as predictors: contingent talks count, months, background, and all interactions; by-dyad random intercepts.

```{r}
ct_lm <- lmer(
  understand ~
    ct_tot *
    months *
    background +
    (1|dyad),
  data = vocab
)
summary(ct_lm)
```

A model with number of understood words as outcome; as predictors: contingent talks count, months, and interaction between the two; by-dyad random intercepts.

```{r}
ct_lm_2 <- lmer(
  understand ~
    ct_tot *
    months +
    (1|dyad),
  data = vocab
)
summary(ct_lm_2)
```

```{r}
plot_model(ct_lm_2, type = "pred", terms = c("ct_tot", "months"))
```

A model with number of understood/said words as outcome; as predictors: contingent talks count, months, and interaction between the two; by-dyad random intercepts.

```{r}
ct_lm_2_undsay <- lmer(
  und_say ~
    ct_tot *
    months +
    (1|dyad),
  data = vocab
)
summary(ct_lm_2_undsay)
```

```{r}
plot_model(ct_lm_2_undsay, type = "pred", terms = c("ct_tot", "months"))
```

# Maternal utterances

A model with number of understood words as outcome; as predictors: maternal utterances count, months, background, and all interactions; by-dyad random intercepts.

```{r}
utt_lm <- lmer(
  understand ~
    utt_tot *
    months *
    background +
    (1|dyad),
  data = vocab
)
summary(utt_lm)
```

A model with number of understood words as outcome; as predictors: maternal utterances count, months, and interaction between the two; by-dyad random intercepts.

```{r}
utt_lm_2 <- lmer(
  understand ~
    utt_tot *
    months +
    (1|dyad),
  data = vocab
)
summary(utt_lm_2)
```

A model with number of understood/said words as outcome; as predictors: maternal utterances count, months, and interaction between the two; by-dyad random intercepts.

```{r}
utt_lm_2_undsay <- lmer(
  und_say ~
    utt_tot *
    months +
    (1|dyad),
  data = vocab
)
summary(utt_lm_2_undsay)
```
