---
title: "Report 1 - Mother utterances data"
date: "23/07/2018"
output: 
  pdf_document: 
    fig_height: 3.5
    fig_width: 5
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.align = "center")
knitr::opts_knit$set(root.dir = normalizePath("../../"))
library(tidyverse)
theme_set(theme_minimal())
```

```{r read-data, message=FALSE}
utterances <- read_csv("./data/utterances.csv") %>%
  mutate_if(is.character, as.factor)

# NAs not removed in sum()
utterances_tot <- utterances %>%
  group_by(dyad, background, months) %>%
  summarise(
    utterances = sum(utterances)
  ) %>%
  ungroup()

point <- read_csv("./data/gestures.csv") %>%
  filter(gesture == "point") %>%
  group_by(dyad, background, months) %>%
  summarise(
    point = sum(count)
  ) %>%
  ungroup() %>%
  mutate_if(is.character, as.factor)

utter <- na.omit(utterances_tot) %>%
  left_join(y = point)
```

# Number of mother utterances

This is how the dataset looks like:

```{r utter}
utterances_tot
```

The utterances have been aggredated within dyad from the counts of the 3 tasks (`five`, `tp1`, `tp2`). There are 125 observations plus 7 missing observations (n = 132). The following graph shows the density distribution of the utterances counts.

```{r density}
utter %>%
  ggplot(aes(utterances)) +
  geom_density() +
  geom_rug() +
  labs(x = "Mother utterances (count)", title = "Density plot of mother uttarances")
```

Number of dyads per background.

```{r n-dyads}
utter %>% group_by(background) %>% summarise(n = n_distinct(dyad))
```

Possibly, Bangladeshi mothers have a lower utterance count than Chinese and English.

```{r background}
utter %>%
  ggplot(aes(utterances, fill = background)) +
  geom_density(alpha = 0.5, colour = NA) +
  geom_rug() +
  labs(x = "Mother utterances (count)")
```

A stripchart shows the same information, but the differences in variance stand out. From higher to lower variance, Bangladeshi > Chinese > English. The is a difference in median of about 100/150 utterances between Bangladeshi on one hand and Chinese/English on the other.

```{r background-jitter}
utter %>%
  ggplot(aes(background, utterances, colour = background)) +
  geom_jitter(width = 0.2) +
  stat_summary(fun.y = median, geom = "point", shape = 18, size = 6, color = "black") +
  labs(y = "Mother utterances (count)", title = "Number of mother utterances by background", subtitle = "The black diamond is the median")
```

The following connected points plot shows that there is no clear pattern of change in number of utterances through visit time. For each dyad, a point is plotted at each visit times (10, 11, 12) and the points of a dyad are connected by a line. The lines show the change within dyads across visit times. Most lines are almost flat.

```{r months}
utter %>%
  ggplot(aes(as.factor(months), utterances, colour = background)) +
  geom_point() +
  geom_line(aes(group = dyad)) +
  facet_grid(background ~ .) +
  labs(x = "Visit time (child age in months)", y = "Mother utterances (count)", title = "Number of mother utterances utterances by visit for\neach background", subtitle = "Each point is a dyad, points of a dyad are connected by a line")
```

# Utterances vs. pointing

```{r utter-point}
utter %>%
  # filter(utterances < 600, point < 30) %>%
  ggplot(aes(utterances, point)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(title = "Correlation between number of utterances and number\nof point gestures", x = "Mother utterances (count)", y = "Point gestures (count)")
```

Is there an interaction between mother utterances and visit time? In the following plot, the effect seems to increase through visit time (although notice wide confidence intervals).

```{r utter-point-months}
utter %>%
  ggplot(aes(utterances, point, colour = as.factor(months))) +
  geom_point() +
  geom_smooth(method = "lm") +
  scale_color_discrete(name = "Visit time (months)") +
  labs(title = "Utterances by point gestures through visit time", x = "Mother utterances (count)", y = "Point gestures (count)")
```

The increase might be driven by the Chinese dyads.

```{r utter-point-background}
utter %>%
  ggplot(aes(utterances, point, colour = as.factor(months))) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(background ~ .) +
  scale_color_discrete(name = "Visit time (months)") +
  labs(title = "Utterances by point gestures through visit time\nby background", x = "Mother utterances (count)", y = "Point gestures (count)")
```
