---
title: "Predicting pointing gestures from HGs, contingent talks, and utterances"
date: "21/08/2018"
output:
  pdf_document:
    fig_height: 3.5
    fig_width: 5
    number_sections: yes
fontsize: 11pt
params:
  version: "v0.9"
  version-date: "21/08/2018"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.align = "center")
knitr::opts_knit$set(root.dir = normalizePath("../../"))
library(fitdistrplus)
library(tidyverse)
theme_set(theme_minimal())
```

```{r read-data, message=FALSE}
gestures <- read_csv("./data/gestures.csv")

gestures_tot <- gestures %>%
  group_by(dyad, background, months, gesture) %>%
  summarise(
    count = sum(count),
    ct = sum(ct)
  ) %>%
  ungroup() %>%
  mutate(
    gesture = factor(gesture, levels = c("reach", "point", "ho_gv"))
  ) %>%
  mutate_if(is.character, as.factor)

utterances <- read_csv("./data/utterances.csv")

# NAs not removed in sum()
utterances_tot <- utterances %>%
  group_by(dyad, background, months) %>%
  summarise(
    utterances = sum(utterances)
  ) %>%
  ungroup() %>%
  mutate_if(is.character, as.factor)

point <- gestures %>%
  filter(gesture == "point") %>%
  group_by(dyad, background, months) %>%
  summarise(
    count = sum(count)
  ) %>%
  ungroup() %>%
  mutate_if(is.character, as.factor)

utter_point <- left_join(utterances_tot, point) %>%
  rename(point = count)

utterances_compl <- utterances %>% na.omit()
utterances_tcompl <- utterances_tot %>% na.omit()

utter_point_lead <- utter_point %>%
  group_by(dyad) %>%
  mutate(
    lead_point = lead(point)
  ) %>%
  filter(months != 12)

hg_point_lead <- gestures_tot %>%
  dplyr::select(-ct) %>%
  spread(gesture, count) %>%
  dplyr::select(-reach) %>%
  group_by(dyad) %>%
  mutate(
    lead_point = lead(point)
  ) %>%
  filter(months != 12)

ct_point_lead <- gestures_tot %>%
  filter(gesture == "point") %>%
  select(-gesture) %>%
  rename(point = count) %>%
  group_by(dyad) %>%
  mutate(
    lead_point = lead(point)
  ) %>%
  filter(months != 12)
```

# Maternal utterancese and infant pointing

There is a very small correlation between number of maternal utterances and the number of point gestures in the following visit.

```{r point-lead-plot, warning=FALSE}
utter_point_lead %>%
  ggplot(aes(utterances, lead_point)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(
    title = "Prediction of number of points based on previous visit\nutterances counts",
    x = "Maternal utterances (count)",
    y = "Infant pointing gestures (count)"
  )
```

There seems to be no major difference between backgrounds.

```{r point-lead-back, warning=FALSE}
utter_point_lead %>%
  ggplot(aes(utterances, lead_point, colour = background)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(
    title = "Prediction of number of points based on previous visit\nutterances counts by background",
    x = "Maternal utterances (count)",
    y = "Infant pointing gestures (count)"
  )
```

# Hold-out and gives and pointing

Hould-out and gives and pointing at next visit do not seem to be correlated, but there are three significant outliers.

```{r hg-point-lead, warning=FALSE}
hg_point_lead %>%
  ggplot(aes(ho_gv, lead_point)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(
    title = "Prediction of number of points based on previous visit\nhould-out and gives",
    x = "Infant hold-out and gves (count)",
    y = "Infant pointing gestures (count)"
  )
```

Possibly, there is a correlation in the English data.

```{r hg-point-lead-regression, warning=FALSE}
hg_point_lead %>%
  ggplot(aes(ho_gv, lead_point, colour = background)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(
    title = "Prediction of number of points based on previous visit\nhould-out and gives by background",
    x = "Infant hold-out and gves (count)",
    y = "Infant pointing gestures (count)"
  )
```

Even when removing outliers, Chinese and Bangladeshi do not show a correlation.

```{r hg-point-lead-regression-2, warning=FALSE}
hg_point_lead %>%
  filter(ho_gv < 20) %>%
  ggplot(aes(ho_gv, lead_point, colour = background)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(
    title = "Prediction of number of points based on previous visit\nhould-out and gives by background",
    subtitle = "Excluding outliers.",
    x = "Infant hold-out and gves (count)",
    y = "Infant pointing gestures (count)"
  )
```

# Maternal contingent talks and infant pointing

There might be a correlation between pointing gestures and maternal contingent talks of the previous visit.

```{r ct-point-lead, warning=FALSE}
ct_point_lead %>%
  ggplot(aes(ct, lead_point)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(
    title = "Prediction of number of points based on previous visit\nmaternal contingent talks",
    x = "Maternal contingent talks (count)",
    y = "Infant pointing gestures (count)"
  )
```

Even when removing outliers, the correlation stays.

```{r ct-point-lead-regression, warning=FALSE}
ct_point_lead %>%
  filter(ct < 20) %>%
  ggplot(aes(ct, lead_point)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(
    title = "Prediction of number of points based on previous visit\nmaternal contingent talks",
    subtitle = "Excluding outliers.",
    x = "Maternal contingent talks (count)",
    y = "Infant pointing gestures (count)"
  )
```

All backgrounds seem to show the correlation (but the Bangladeshi data is quite scant at higher CT counts).

```{r ct-point-lead-regression-background, warning=FALSE}
ct_point_lead %>%
  filter(ct < 20) %>%
  ggplot(aes(ct, lead_point, colour = background)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(
    title = "Prediction of number of points based on previous visit\nmaternal contingent talks by background",
    subtitle = "Excluding outliers.",
    x = "Maternal contingent talks (count)",
    y = "Infant pointing gestures (count)"
  )
```

# General observations

For the cases that show a correlation, it must be noted that the confidence intervals are in general quite wide, meaning that we are not very sure about the presence of said correlations.

Another issue is that there are a lot of counts = 0, then a few data points with counts between 1 and 7.
