---
title: "Statistical testing II"
date: "08/10/2018"
output:
  pdf_document:
    fig_height: 3.5
    fig_width: 5
    number_sections: yes
fontsize: 11pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = normalizePath("../../"))
library(MASS)
library(tidyverse)
theme_set(theme_minimal())
library(itsadug)
library(tidymv)
library(lmerTest)
library(effects)
library(simr)
```

```{r read-data, message=FALSE, echo=FALSE}
gestures <- read_csv("./data/gestures.csv")

gestures_tot <- gestures %>%
  group_by(dyad, background, months, gesture) %>%
  summarise(
    count = sum(count),
    ct = sum(ct)
  ) %>%
  ungroup() %>%
  mutate(
    gesture = factor(gesture, levels = c("reach", "point", "ho_gv"))
  ) %>%
  mutate_if(is.character, as.factor) %>%
  mutate(
    back_o = ordered(background, levels = c("English", "Bangladeshi", "Chinese"))
  )

contrasts(gestures_tot$back_o) <- "contr.treatment"

utterances <- read_csv("./data/utterances.csv")

# NAs not removed in sum()
utterances_tot <- utterances %>%
  group_by(dyad, background, months) %>%
  summarise(
    utterances = sum(utterances)
  ) %>%
  ungroup() %>%
  mutate_if(is.character, as.factor) %>%
  mutate(
    back_o = ordered(background, levels = c("English", "Bangladeshi", "Chinese"))
  )

contrasts(utterances_tot$back_o) <- "contr.treatment"

hg_tot <- filter(gestures_tot, gesture == "ho_gv")
reach_tot <- filter(gestures_tot, gesture == "reach")
point_tot <- filter(gestures_tot, gesture == "point")
all_tot <- gestures_tot %>%
  group_by(dyad, back_o, months) %>%
  summarise(count = sum(count), ct = sum(ct))

hg_point_lead <- gestures_tot %>%
  dplyr::select(-ct) %>%
  spread(gesture, count) %>%
  dplyr::select(-reach) %>%
  group_by(dyad) %>%
  mutate(
    lead_point = lead(point)
  ) %>%
  filter(months != 12)

reach_point_lead <- gestures_tot %>%
  dplyr::select(-ct) %>%
  spread(gesture, count) %>%
  dplyr::select(-ho_gv) %>%
  group_by(dyad) %>%
  mutate(
    lead_point = lead(point)
  ) %>%
  filter(months != 12)

reach_point_lead <- gestures_tot %>%
  dplyr::select(-ct) %>%
  spread(gesture, count) %>%
  dplyr::select(-ho_gv) %>%
  group_by(dyad) %>%
  mutate(
    lead_point = lead(point)
  ) %>%
  filter(months != 12)

ct_point_lead <- gestures_tot %>%
  filter(gesture == "point") %>%
  dplyr::select(-gesture) %>%
  rename(point = count) %>%
  group_by(dyad) %>%
  mutate(
    lead_point = lead(point)
  ) %>%
  filter(months != 12)

utter_point_lead <- gestures_tot %>%
  filter(gesture == "point") %>%
  right_join(y = utterances_tot) %>%
  group_by(dyad) %>%
  mutate(
    lead_point = lead(count)
  ) %>%
  filter(months != 12)
```

This report presents the results from generalised additive models which test the development and background differences of infant gestures and maternal sentence counts.

# Hold out and gives

```{r hg-gam, echo=FALSE, message=FALSE, include=FALSE}
hg_gam <- gam(
  count ~
    back_o +
    s(months, k = 3) +
    s(months, k = 3, by = back_o) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = hg_tot,
  method = "ML",
  family = negbin(0.6434)
)

hg_gam_null <- gam(
  count ~
    # back_o +
    s(months, k = 3) +
    # s(months, k = 3, by = back_o) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = hg_tot,
  method = "ML",
  family = negbin(0.6434)
)

hg_gam_2 <- gam(
  count ~
    s(months, k = 3) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = hg_tot,
  method = "ML",
  family = negbin(0.1946)
)
hg_gam_2_null <- gam(
  count ~
    # s(months, k = 3) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = hg_tot,
  method = "ML",
  family = negbin(0.1946)
)
compareML(hg_gam_2_null, hg_gam_2)
```

According to a GAM model, background is not a significant predictor of HoGs counts over time. This means that according to the model there are no differences in HoGs development between backgrounds (p = 0.179).

```{r hg-compare-1, echo=FALSE}
compareML(hg_gam_null, hg_gam)
```

On the other hand, the time of visit is a significant predictor. HoG counts increase over time by an estimate of 1 HoGs every 2 months (so that at visit time 3 on average infants produce 1 more gesture than visit time 1, p = 0.015).

```{r hg-compare-2, echo=FALSE}
compareML(hg_gam_2_null, hg_gam_2)
```

```{r hg-gam-plot, echo=FALSE}
plot_smooths(hg_gam_2, months, series_length = 25) +
  labs(title = "Estimated development of HoG counts over visit time\n(months 10, 11, 12)")
```

# Reaches

```{r reach-gam, echo=FALSE, message=FALSE, include=FALSE}
reach_gam <- gam(
  count ~
    back_o +
    s(months, k = 3) +
    s(months, k = 3, by = back_o) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = reach_tot,
  method = "ML",
  family = negbin(0.986)
)

reach_gam_null <- gam(
  count ~
    # back_o +
    s(months, k = 3) +
    # s(months, k = 3, by = back_o) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = reach_tot,
  method = "ML",
  family = negbin(0.986)
)

reach_gam_2 <- gam(
  count ~
    s(months, k = 3) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = reach_tot,
  method = "ML",
  family = negbin(0.1946)
)
reach_gam_2_null <- gam(
  count ~
    # s(months, k = 3) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = reach_tot,
  method = "ML",
  family = negbin(0.1946)
)
```

According to GAMs, neither visit time nor background are significant predictors of reach counts (p = 0.466, p = 0.842 respectively).

```{r reach-compare-1}
compareML(reach_gam_null, reach_gam)
```

```{r reach-compare-2}
compareML(reach_gam_2_null, reach_gam_2)
```

# Points

```{r point-gam, echo=FALSE, message=FALSE, include=FALSE}
point_nb <- glm.nb(count ~ months, data = point_tot)

point_gam <- gam(
  count ~
    back_o +
    s(months, k = 3) +
    s(months, k = 3, by = back_o) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = point_tot,
  method = "ML",
  family = negbin(0.1946)
)

point_gam_null <- gam(
  count ~
    # back_o +
    s(months, k = 3) +
    # s(months, k = 3, by = back_o) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = point_tot,
  method = "ML",
  family = negbin(0.1946)
)

point_gam_2 <- gam(
  count ~
    s(months, k = 3) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = point_tot,
  method = "ML",
  family = negbin(0.1946)
)
point_gam_2_null <- gam(
  count ~
    # s(months, k = 3) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = point_tot,
  method = "ML",
  family = negbin(0.1946)
)
```

Background is not a significant predictor of reach gestures development (p = 0.715).

```{r point-compare-1}
compareML(point_gam_null, point_gam)
```

Visit time is a significant predictor of reaches development (p = 0.011), and reaches counts increase over time by an estimate of 1 reach every 2 months (so that at visit time 3 on average infants produce 1 more gesture than visit time 1).

```{r point-compare-2}
compareML(point_gam_2_null, point_gam_2)
```

```{r point-gam-plot, echo=FALSE}
plot_smooths(point_gam_2, months, series_length = 25) +
  labs(title = "Estimated development of point counts over visit time\n(months 10, 11, 12)")
```

# Maternal utterances and contingent talks

Background nor visit time are significant predictors of the development of counts over time of maternal utterances and contingent talks.

# Summary

Background is not a significant predictor in any of the models. Visit time is a significant predictor for hold out and gives, and pointing gestures, but not for reach gestures, nor maternal counts. In general, there is an increase of 1 HoG/pointing between visit time 1 and 3.
