---
title: "Statistical analysis"
output:
  pdf_document:
    highlight: tango
    keep_tex: yes
    latex_engine: xelatex
    number_sections: yes
mainfont: Lato
params:
  version: "2.0"
  version-date: "2019/09/17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
knitr::opts_knit$set(root.dir = normalizePath("../"))
library(MASS)
library(tidyverse)
theme_set(theme_minimal())
library(itsadug)
library(tidymv) # https://github.com/stefanocoretta/tidymv
library(lmerTest)
library(effects)
library(simr)
library(sjPlot)
```

# Read data

These chunks read the data and processes it for analysis.

The following reads `gestures.csv` and `utterances.csv` into `gesture_tot` and `utterances_tot`.
`gestures_tot` has time series data of infant gestures and maternal Contingent Talks at 10, 11, and 12 months. `utterance_tot` has time series data of maternal utterances at 10, 11, and 12 months. Data is aggregated from the two experimental activities.

```{r read-data, message=FALSE, cache=FALSE, message=FALSE, warning=FALSE}
gestures <- read_csv("./data/gestures.csv")

gestures_tot <- gestures %>%
  group_by(dyad, background, months, gesture) %>%
  summarise(
    count = sum(count),
    ct = sum(ct)
  ) %>%
  ungroup() %>%
  mutate(
    gesture = factor(gesture, levels = c("reach", "point", "ho_gv"))
  ) %>%
  mutate_if(is.character, as.factor) %>%
  mutate(
    # Needed for GAMs
    back_o = ordered(background, levels = c("English", "Bengali", "Chinese"))
  )

# Needed for GAMs
contrasts(gestures_tot$back_o) <- "contr.treatment"

utterances <- read_csv("./data/utterances.csv")

utterances_tot <- utterances %>%
  group_by(dyad, background, months) %>%
  summarise(
    utterances = sum(utterances) # there are NAs that must be kept
  ) %>%
  ungroup() %>%
  mutate_if(is.character, as.factor) %>%
  mutate(
    # Needed for GAMs
    back_o = ordered(background, levels = c("English", "Bengali", "Chinese"))
  )

# Needed for GAMs
contrasts(utterances_tot$back_o) <- "contr.treatment"
```

Here we create individual datasets for HoGs, reaches, pointing, and a dataset with aggreagated gestures count and maternal contingent talks (`all_tot`).

```{r sep-counts, message=FALSE, cache=FALSE, message=FALSE, warning=FALSE}
hg_tot <- filter(gestures_tot, gesture == "ho_gv")
reach_tot <- filter(gestures_tot, gesture == "reach")
point_tot <- filter(gestures_tot, gesture == "point")

# Count = all gestures count, CT is aggregated from all gestures types
all_tot <- gestures_tot %>%
  group_by(dyad, back_o, months) %>%
  summarise(count = sum(count), ct = sum(ct))
```

The following code creates datasets for the analysis of pointing as predicted by HoGs, reaches, maternal CTs, and maternal utterances. The datasets are constructed so that the count of pointing at 11 months is matched with the count of gesture/utterances at 10 months, and the pointing at 12 is matched with the count of gesture/utterances at 11 months. Pointing at 10 months is dropped (since there is no data at 9 months).

```{r point-lead, message=FALSE, cache=FALSE, message=FALSE, warning=FALSE}
hg_point_lead <- gestures_tot %>%
  dplyr::select(-ct) %>%
  spread(gesture, count) %>%
  dplyr::select(-reach) %>%
  group_by(dyad) %>%
  mutate(
    lead_point = lead(point)
  ) %>%
  filter(months != 12)

reach_point_lead <- gestures_tot %>%
  dplyr::select(-ct) %>%
  spread(gesture, count) %>%
  dplyr::select(-ho_gv) %>%
  group_by(dyad) %>%
  mutate(
    lead_point = lead(point)
  ) %>%
  filter(months != 12)

ct_point_lead <- gestures_tot %>%
  filter(gesture == "point") %>%
  dplyr::select(-gesture) %>%
  rename(point = count) %>%
  group_by(dyad) %>%
  mutate(
    lead_point = lead(point)
  ) %>%
  filter(months != 12)

utter_point_lead <- gestures_tot %>%
  filter(gesture == "point") %>%
  right_join(y = utterances_tot) %>%
  group_by(dyad) %>%
  mutate(
    lead_point = lead(count)
  ) %>%
  filter(months != 12)
```

The following creates a dataset with the infants' vocabulary counts and total counts of all gestures, HoGs + point, reaches, maternal utterances and maternal contingent talks.

```{r vocab, message=FALSE, cache=FALSE, message=FALSE, warning=FALSE}
hgp_tot <- gestures_tot %>%
  filter(gesture != "reach") %>%
  group_by(dyad, background) %>%
  summarise(hgp_tot = sum(count))

reach_tot_2 <- gestures_tot %>%
  filter(gesture == "reach") %>%
  group_by(dyad, background) %>%
  summarise(reach_tot = sum(count))

vocab_gest <- gestures_tot %>%
  group_by(dyad, background) %>%
  summarise(count_tot = sum(count), ct_tot = sum(ct)) %>%
  ungroup() %>%
  full_join(y = hgp_tot) %>%
  full_join(y = reach_tot_2) %>%
  mutate_if(is.factor, as.character)

vocab_utt <- utterances_tot %>%
  group_by(dyad, background) %>%
  summarise(utt_tot = sum(utterances)) %>%
  ungroup() %>%
  mutate_if(is.factor, as.character)

vocab <- read_csv("./data/vocab.csv") %>%
  full_join(y = vocab_gest) %>%
  full_join(y = vocab_utt) %>%
  arrange(dyad, months) %>%
  mutate(
    months = as.factor(months),
    background = factor(background, levels = c("English", "Bengali", "Chinese"))
  ) %>%
  mutate_if(is.character, as.factor)
```

\newpage

# Analysis 1a. The development of reaches, hold out and gives (HoGs), and points from 10-12 months.

For analysis 1a, we fitted a series of GAMMs using the negative binomial function.
The choice of using the negative binomial rather than the Poisson distribution is justified by the overdispersion of the data (and the very long tail in the distribution).
The negative binomial distribution requires the specification of the theta parameter.
The parameter has been estimated from the data by fitting a generalised linear model with the negative binomial distribution using `MASS::glm.nb`.

Cultural background and development (within the 10-12 months sampling period) were tested separately with two series of models for each gesture (HoGs, reaches, pointing) and maternal scores (maternal utterances and maternal contingent talks). To test the significance of background and development we compared a full model including the relevant parameter with one in which the parameter is dropped, using `itsadug::compareML()`.

The full models testing background contain the following terms: a parametric term for background (`back_o`), a reference smooth over sampling period (`s(months)`, 10-12), a difference smooth over sampling period by background (`s(months, by = back_o)`), and a random smooth over sampling period by infant (`s(months, dyad)`, this corresponds to LME random smooths and intercepts). The reference smooth corresponds to the smooth of development in English infants, while the difference smooth models the difference between the smooth of English infants and those of Bengali and Chinese infants.

The full models testing development contain the following terms: a smooth over sampling period and a random smooth over sampling period by infant (`s(months, dyad)`, this corresponds to LME random smooths and intercepts).

The null models for background drop all terms including background (`back_o`) while the null models for development drop the smooth over sampling period (`s(months)`), but keep the random smooths (comparison can be done either on the fixed effect structure or the random effects structure at a time).

The warnings about repeated 1-d smooths do not indicate problems with the models, but they only inform the user about multiple smooths over the same variable (which are needed).

## Reaches development

```{r reaches, warning=FALSE}
reach_tot %>%
  ggplot(aes(count)) + geom_density() + geom_rug(alpha = 0.1) +
  labs(
    title = "Distribution of the count of reaches",
    x = "Count of infant reaches"
  )
```

----

The following models test cultural group for infant reaches.

```{r reach-gam}
# Estimation of theta for the negbin() family
reach_nb <- glm.nb(count ~ months, data = reach_tot)
theta <- summary(reach_nb)[["theta"]]

reach_gam <- gam(
  count ~
    # parametric term
    back_o +
    # reference smooth
    s(months, k = 3) +
    # difference smoth
    s(months, k = 3, by = back_o) +
    # random smooths (random effect)
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = reach_tot,
  method = "ML",
  family = negbin(theta)
)
summary(reach_gam)

reach_gam_null <- gam(
  count ~
    # back_o +
    s(months, k = 3) +
    # s(months, k = 3, by = back_o) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = reach_tot,
  method = "ML",
  family = negbin(theta)
)

compareML(reach_gam_null, reach_gam)
```

```{r reach-gam-plot}
plot_smooths(reach_gam, months, facet_terms = back_o, series_length = 25, transform = exp) +
  labs(x = "Months", y = "Count of reaches", title = "Predicted development of reaches by background")
```

----

The following models test the development of infant reaches.

```{r reach-gam-2}
reach_gam_2 <- gam(
  count ~
    s(months, k = 3) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = reach_tot,
  method = "ML",
  family = negbin(theta)
)
reach_gam_2_null <- gam(
  count ~
    # s(months, k = 3) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = reach_tot,
  method = "ML",
  family = negbin(theta)
)
compareML(reach_gam_2_null, reach_gam_2)
```

```{r reach-gam-2-plot}
plot_smooths(reach_gam_2, months, series_length = 25, transform = exp) +
  labs(x = "Months", y = "Count of reaches", title = "Predicted development of reaches")
```

## HGs development

```{r hog, warning=FALSE}
hg_tot %>%
  ggplot(aes(count)) + geom_density() + geom_rug(alpha = 0.1) +
  labs(
    title = "Distribution of the count of HoGs",
    x = "Count of infant HoGs"
  )
```

----

The following models test cultural group differences for infant HoGs.

```{r hg-gam}
hg_nb <- glm.nb(count ~ months, data = hg_tot)
theta_2 <- summary(hg_nb)[["theta"]]

hg_gam <- gam(
  count ~
    back_o +
    s(months, k = 3) +
    s(months, k = 3, by = back_o) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = hg_tot,
  method = "ML",
  family = negbin(theta_2)
)
summary(hg_gam)

hg_gam_null <- gam(
  count ~
    # back_o +
    s(months, k = 3) +
    # s(months, k = 3, by = back_o) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = hg_tot,
  method = "ML",
  family = negbin(theta_2)
)

compareML(hg_gam_null, hg_gam)
```

```{r hg-gam-plot}
plot_smooths(hg_gam, months, facet_terms = back_o, series_length = 25, transform = exp) +
  labs(x = "Months", y = "Count of HoGs", title = "Predicted development of HoGs by background")
```

----

The following models test development of infant HoGs.

```{r hg-gam-2}
hg_gam_2 <- gam(
  count ~
    s(months, k = 3) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = hg_tot,
  method = "ML",
  family = negbin(theta_2)
)
hg_gam_2_null <- gam(
  count ~
    # s(months, k = 3) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = hg_tot,
  method = "ML",
  family = negbin(theta_2)
)
compareML(hg_gam_2_null, hg_gam_2)
```

```{r hg-gam-2-plot}
plot_smooths(hg_gam_2, months, series_length = 25, transform = exp) +
  labs(x = "Months", y = "Count of HoGs", title = "Predicted development of HoGs")
```

## Points development

```{r points, warning=FALSE}
point_tot %>%
  ggplot(aes(count)) + geom_density() + geom_rug(alpha = 0.1) +
  labs(
    title = "Distribution of the count of points",
    x = "Count of infant points"
  )
```

----

The following models test cultural group differences in infant pointing.

```{r point-gam}
point_nb <- glm.nb(count ~ months, data = point_tot)
theta_3 <- summary(point_nb)[["theta"]]

point_gam <- gam(
  count ~
    back_o +
    s(months, k = 3) +
    s(months, k = 3, by = back_o) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = point_tot,
  method = "ML",
  family = negbin(theta_3)
)
summary(point_gam)

point_gam_null <- gam(
  count ~
    # back_o +
    s(months, k = 3) +
    # s(months, k = 3, by = back_o) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = point_tot,
  method = "ML",
  family = negbin(theta_3)
)

compareML(point_gam_null, point_gam)
```

```{r point-gam-plot}
plot_smooths(point_gam, months, facet_terms = back_o, series_length = 25, transform = exp) +
  labs(x = "Months", y = "Count of points", title = "Predicted development of points by background")
```

----

The following models test development of infant pointing.

```{r point-gam-2}
point_gam_2 <- gam(
  count ~
    s(months, k = 3) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = point_tot,
  method = "ML",
  family = negbin(theta_3)
)
point_gam_2_null <- gam(
  count ~
    # s(months, k = 3) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = point_tot,
  method = "ML",
  family = negbin(theta_3)
)
compareML(point_gam_2_null, point_gam_2)
```

```{r point-gam-2-plot}
plot_smooths(point_gam_2, months, series_length = 25, transform = exp) +
  labs(x = "Months", y = "Count of points", title = "Predicted development of points")
```

\newpage

# Analysis 1b. Frequency of maternal utterances and contingent talk to infants aged 10-12 months.

For maternal utterances we used a normal distribution, since the distribution of the data was almost normal.
For maternal contingent talks instead we used again the negative binomial distribution for the same reasons as above.

## Maternal utterances development

```{r utterances, warning=FALSE}
utterances_tot %>%
  ggplot(aes(utterances)) + geom_density() + geom_rug(alpha = 0.1) +
  labs(
    title = "Distribution of the count of utterances",
    x = "Count of maternal utterances"
  )
```

----

The following models test cultural group.

```{r utter-gam}
utter_gam <- gam(
  utterances ~
    back_o +
    s(months, k = 3) +
    s(months, k = 3, by = back_o) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = utterances_tot,
  method = "ML"
)
summary(utter_gam)

utter_gam_null <- gam(
  utterances ~
    # back_o +
    s(months, k = 3) +
    # s(months, k = 3, by = back_o) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = utterances_tot,
  method = "ML"
)

compareML(utter_gam_null, utter_gam)
```

```{r utter-gam-plot}
plot_smooths(utter_gam, months, facet_terms = back_o, series_length = 10) +
  labs(x = "Months", y = "Count of utterances", title = "Predicted development of utterances by background")
```

----

The following models test time sample.

```{r utter-gam-2}
utter_gam_2 <- gam(
  utterances ~
    s(months, k = 3) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = utterances_tot,
  method = "ML"
)

utter_gam_2_null <- gam(
  utterances ~
    # s(months, k = 3) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = utterances_tot,
  method = "ML"
)

compareML(utter_gam_2_null, utter_gam_2)
```

```{r utter-gam-2-plot}
plot_smooths(utter_gam_2, months, series_length = 10) +
  labs(x = "Months", y = "Count of utterances", title = "Predicted development of utterances")
```

## Contingent talks development

```{r ct, warning=FALSE}
all_tot %>%
  ggplot(aes(ct)) + geom_density() + geom_rug(alpha = 0.1) +
  labs(
    title = "Distribution of the count of CTs",
    x = "Count of maternal CTs"
  )
```

----

The following models test cultural group.

```{r ct-gam}
ct_nb <- glm.nb(ct ~ months, data = all_tot)
theta_4 <- summary(ct_nb)[["theta"]]

ct_gam <- gam(
  ct ~
    back_o +
    s(months, k = 3) +
    s(months, k = 3, by = back_o) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = all_tot,
  method = "ML",
  family = negbin(theta_4)
)
summary(ct_gam)

ct_gam_null <- gam(
  ct ~
    # back_o +
    s(months, k = 3) +
    # s(months, k = 3, by = back_o) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = all_tot,
  method = "ML",
  family = negbin(theta_4)
)

compareML(ct_gam_null, ct_gam)
```

```{r ct-gam-plot}
plot_smooths(ct_gam, months, facet_terms = back_o, series_length = 10, transform = exp) +
  labs(x = "Months", y = "Count of CTs", title = "Predicted development of CTs by background")
```

----

The following models test time sample.

```{r ct-gam-2}
ct_gam_2 <- gam(
  count ~
    s(months, k = 3) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = all_tot,
  method = "ML",
  family = negbin(theta_4)
)

ct_gam_2_null <- gam(
  count ~
    # s(months, k = 3) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = all_tot,
  method = "ML",
  family = negbin(theta_4)
)

compareML(ct_gam_2_null, ct_gam_2)
```

```{r ct-gam-2-plot}
plot_smooths(ct_gam_2, months, series_length = 10, transform = exp) +
  labs(x = "Months", y = "Count of CTs", title = "Predicted development of CTs")
```

\newpage

# Analysis 1c. Predictors of pointing

The following GLMMs test the relation between pointing and reaches/HoGs. The count of pointing refers to the one produced by the infant in the subsequent session: For example, the count of reaches at 10 months is matched with the count of points at 11 months, and that of reaches at 11 months is matched with the count of points at 12 months. This allows us to test whether gestures at a certain sampling time predict the production of pointing at the next sampling time. Data on pointing at 10 months is dropped, since there is no data on gestures prior to 10 months.

## Reaches

```{r reach-point-lm}
reach_point_lead_nb <- glm.nb(lead_point ~ reach, data = reach_point_lead)
theta_5 <- summary(reach_point_lead_nb)[["theta"]]

reach_point_lm <- glmer(
  lead_point ~
    reach *
    background +
    (1|dyad),
  data = reach_point_lead,
  family = negbin(theta_5)
)
summary(reach_point_lm)
```

```{r reach-point-plot}
plot_model(reach_point_lm, type = "pred", terms = c("reach", "background"))
```

## HoGs

```{r hg-point-lm}
hg_point_lead_nb <- glm.nb(lead_point ~ ho_gv, data = filter(hg_point_lead, ho_gv < 20))
theta_6 <- summary(reach_point_lead_nb)[["theta"]]

hg_point_lm <- glmer(
  lead_point ~
    ho_gv *
    background +
    (1|dyad),
  data = filter(hg_point_lead, ho_gv < 20),
  family = negbin(theta_6)
)
summary(hg_point_lm)
```

```{r hg-point-plot}
plot_model(hg_point_lm, type = "pred", terms = c("ho_gv", "background"))
```

\newpage

# Analysis 2. Predictors of vocabulary scores at 12 and 18 months

## Comprehension at 12 and 18 months

### All gestures combined

```{r all-gest-lm}
all_gest_lm <- glm(
  comprehension ~
    count_tot *
    months *
    background,
  data = vocab
)
summary(all_gest_lm)
```

```{r all-gest-lm-plot}
plot_model(all_gest_lm, type = "pred", terms = c("count_tot", "months", "background"))
```

### HoGs + points

```{r hgp-lm}
hgp_lm <- glm(
  comprehension ~
    hgp_tot *
    months *
    background,
  data = vocab
)
summary(hgp_lm)
```

```{r hgp-lm-2-plot}
plot_model(hgp_lm, type = "pred", terms = c("hgp_tot", "months", "background"))
```

### Reaches

```{r reach-lm}
reach_lm <- glm(
  comprehension ~
    reach_tot *
    months *
    background,
  data = vocab
)
summary(reach_lm)
```

```{r reach-lm-2-plot}
plot_model(reach_lm, type = "pred", terms = c("reach_tot", "months", "background"))
```

### Maternal utterances

```{r utt-lm}
utt_lm <- glm(
  comprehension ~
    utt_tot *
    months *
    background,
  data = vocab
)
summary(utt_lm)
```

```{r utt-lm-2-plot}
plot_model(utt_lm, type = "pred", terms = c("utt_tot", "months", "background"))
```

### Contingent talks

```{r ct-lm}
ct_lm <- glm(
  comprehension ~
    ct_tot *
    months *
    background,
  data = filter(vocab, ct_tot < 30)
)
summary(ct_lm)
```

```{r ct-lm-2-plot}
plot_model(ct_lm, type = "pred", terms = c("ct_tot", "months", "background"))
```

## Production at 12 and 18 months

### All gestures combined

```{r all-gest-lm-2-undsay}
all_gest_prod <- glm(
  production ~
    count_tot *
    months *
    background,
  data = vocab
)
summary(all_gest_prod)
```

```{r all-gest-lm-2-undsay-plot}
plot_model(all_gest_prod, type = "pred", terms = c("count_tot", "months", "background"))
```

### HoGs + point

```{r hgp-lm-2-undsay}
hgp_prod <- glm(
  production ~
    hgp_tot *
    months *
    background,
  data = vocab
)
summary(hgp_prod)
```

```{r hgp-lm-2-undsay-plot}
plot_model(hgp_prod, type = "pred", terms = c("hgp_tot", "months", "background"))
```

### Reaches

```{r reach-lm-2-undsay}
reach_prod <- glm(
  production ~
    reach_tot *
    months *
    background,
  data = vocab
)
summary(reach_prod)
```

```{r reach-lm-2-undsay-plot}
plot_model(reach_prod, type = "pred", terms = c("reach_tot", "months", "background"))
```

### Maternal utterances

```{r utt-lm-2-undsay}
utt_prod <- glm(
  production ~
    utt_tot *
    months *
    background,
  data = vocab
)
summary(utt_prod)
```

```{r utt-lm-2-undsay-plot}
plot_model(utt_prod, type = "pred", terms = c("utt_tot", "months", "background"))
```

### Contingent talks

```{r ct-lm-2-undsay}
ct_prod <- glm(
  production ~
    ct_tot *
    months *
    background,
  data = filter(vocab, ct_tot < 30)
)
summary(ct_prod)
```

```{r ct-lm-2-undsay-plot}
plot_model(ct_prod, type = "pred", terms = c("ct_tot", "months", "background"))
```

\newpage

# Number of observations

The following sections report the number of observations (excluding NAs) used in the models above.

## Analysis 1a

### Reaches

```{r reaches-obs}
reach_tot %>%
  group_by(back_o, months) %>%
  na.omit() %>%
  summarise(n = n())
```

### HoGs

```{r hg-obs}
hg_tot %>%
  group_by(back_o, months) %>%
  na.omit() %>%
  summarise(n = n())
```

### Points

```{r point-obs}
point_tot %>%
  group_by(back_o, months) %>%
  na.omit() %>%
  summarise(n = n())
```

## Analysis 1b

### Maternal utterances

```{r utter-obs}
utterances_tot %>%
  group_by(back_o, months) %>%
  na.omit() %>%
  summarise(n = n())
```

### Maternal CTs

```{r ct-obs}
all_tot %>%
  group_by(back_o, months) %>%
  na.omit() %>%
  summarise(n = n())
```

## Analysis 1c

### Reaches

```{r reachpoint-obs}
reach_point_lead %>%
  group_by(back_o) %>%
  na.omit() %>%
  summarise(n = n())
```

### HoGs

```{r hgpoint-obs}
hg_point_lead %>%
  group_by(back_o) %>%
  na.omit() %>%
  summarise(n = n())
```

## Analysis 2

The counts apply both to the comprehension and production analyses.

```{r vocab-obs}
vocab %>%
  group_by(background) %>%
  na.omit() %>%
  summarise(n = n())
```

# Correlation of vocabulary scores and maternal scores

```{r vocab-cor}
vocab %>%
  ggplot(aes(comprehension, production)) +
  geom_point() +
  geom_smooth(method = "glm", method.args = list(family = poisson))
```

```{r maternal-cor}
all_tot %>%
  left_join(utterances_tot) %>%
  ggplot(aes(utterances, ct)) +
  geom_point() +
  geom_smooth(method = "glm", method.args = list(family = poisson))
```


# R session

```{r session}
sessionInfo()
```
