---
title: "Supplement"
output: 
  pdf_document: 
    highlight: tango
    latex_engine: xelatex
    number_sections: yes
mainfont: Lato
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
knitr::opts_knit$set(root.dir = normalizePath("../"))
library(MASS)
library(tidyverse)
theme_set(theme_minimal())
library(itsadug)
library(tidymv) # https://github.com/stefanocoretta/tidymv
library(lmerTest)
library(effects)
library(simr)
library(sjPlot)
```

# Read data

These chunks read the data and processes it for analysis.

The following reads `gestures.csv` and `utterances.csv` into `gesture_tot` and `utterances_tot`.
`gestures_tot` has time series data of infant gestures and maternal Contingent Talks at 10, 11, and 12 months. `utterance_tot` has time series data of maternal utterances at 10, 11, and 12 months. Data is aggregated from the two experimental activities.

```{r read-data, message=FALSE, cache=FALSE, message=FALSE, warning=FALSE}
gestures <- read_csv("./data/gestures.csv")

gestures_tot <- gestures %>%
  group_by(dyad, background, months, gesture) %>%
  summarise(
    count = sum(count),
    ct = sum(ct)
  ) %>%
  ungroup() %>%
  mutate(
    gesture = factor(gesture, levels = c("reach", "point", "ho_gv"))
  ) %>%
  mutate_if(is.character, as.factor) %>%
  mutate(
    # Needed for GAMs
    back_o = ordered(background, levels = c("English", "Bengali", "Chinese"))
  )

# Needed for GAMs
contrasts(gestures_tot$back_o) <- "contr.treatment"

utterances <- read_csv("./data/utterances.csv")

utterances_tot <- utterances %>%
  group_by(dyad, background, months) %>%
  summarise(
    utterances = sum(utterances) # there are NAs that must be kept
  ) %>%
  ungroup() %>%
  mutate_if(is.character, as.factor) %>%
  mutate(
    # Needed for GAMs
    back_o = ordered(background, levels = c("English", "Bengali", "Chinese"))
  )

# Needed for GAMs
contrasts(utterances_tot$back_o) <- "contr.treatment"
```

Here we create individual datasets for HoGs, reaches, pointing, and a dataset with aggreagated gestures count and maternal contingent talks (`all_tot`).

```{r sep-counts}
hg_tot <- filter(gestures_tot, gesture == "ho_gv")
reach_tot <- filter(gestures_tot, gesture == "reach")
point_tot <- filter(gestures_tot, gesture == "point")

# Count = all gestures count, CT is aggregated from all gestures types
all_tot <- gestures_tot %>%
  group_by(dyad, back_o, months) %>%
  summarise(count = sum(count), ct = sum(ct))
```

The following code creates datasets for the analysis of pointing as predicted by HoGs, reaches, maternal CTs, and maternal utterances. The datasets are constructed so that the count of pointing at 11 months is matched with the count of gesture/utterances at 10 months, and the pointing at 12 is matched with the count of gesture/utterances at 11 months. Pointing at 10 months is dropped (since there is no data at 9 months).

```{r point-lead}
hg_point_lead <- gestures_tot %>%
  dplyr::select(-ct) %>%
  spread(gesture, count) %>%
  dplyr::select(-reach) %>%
  group_by(dyad) %>%
  mutate(
    lead_point = lead(point)
  ) %>%
  filter(months != 12)

reach_point_lead <- gestures_tot %>%
  dplyr::select(-ct) %>%
  spread(gesture, count) %>%
  dplyr::select(-ho_gv) %>%
  group_by(dyad) %>%
  mutate(
    lead_point = lead(point)
  ) %>%
  filter(months != 12)

ct_point_lead <- gestures_tot %>%
  filter(gesture == "point") %>%
  dplyr::select(-gesture) %>%
  rename(point = count) %>%
  group_by(dyad) %>%
  mutate(
    lead_point = lead(point)
  ) %>%
  filter(months != 12)

utter_point_lead <- gestures_tot %>%
  filter(gesture == "point") %>%
  right_join(y = utterances_tot) %>%
  group_by(dyad) %>%
  mutate(
    lead_point = lead(count)
  ) %>%
  filter(months != 12)
```

The following creates a dataset with the infants' vocabulary counts and total counts of all gestures, HoGs + point, reaches, maternal utterances and maternal contingent talks.

```{r vocab}
hgp_tot <- gestures_tot %>%
  filter(gesture != "reach") %>%
  group_by(dyad, background) %>%
  summarise(hgp_tot = sum(count))

reach_tot_2 <- gestures_tot %>%
  filter(gesture == "reach") %>%
  group_by(dyad, background) %>%
  summarise(reach_tot = sum(count))

vocab_gest <- gestures_tot %>%
  group_by(dyad, background) %>%
  summarise(count_tot = sum(count), ct_tot = sum(ct)) %>%
  ungroup() %>%
  full_join(y = hgp_tot) %>%
  full_join(y = reach_tot_2) %>%
  mutate_if(is.factor, as.character)

vocab_utt <- utterances_tot %>%
  group_by(dyad, background) %>%
  summarise(utt_tot = sum(utterances)) %>%
  ungroup() %>%
  mutate_if(is.factor, as.character)

vocab <- read_csv("./data/vocab.csv") %>%
  full_join(y = vocab_gest) %>%
  full_join(y = vocab_utt) %>%
  arrange(dyad, months) %>%
  mutate(
    months = as.factor(months),
    background = factor(background, levels = c("English", "Bengali", "Chinese"))
  ) %>%
  mutate_if(is.character, as.factor)
```

\newpage

# Analysis 1a. The development of reaches, hold out and gives (HoGs), and points from 10-12 months.

For analysis 1a, we fitted a series of GAMMs using the negative binomial function.
The choice of using the negative binomial rather than the Poisson distribution is justified by the overdispersion of the data (and the very long tail in the distribution).
The negative binomial distribution requires the specification of the theta parameter.
The parameter has been estimated from the data by fitting a generalised linear model with the negative binomial distribution using `MASS::glm.nb`.

## Reaches development

The following models test cultural group.

```{r reach-gam}
# Estimation of theta for the negbin() family
reach_nb <- glm.nb(count ~ months, data = reach_tot)
theta <- summary(reach_nb)[["theta"]]

reach_gam <- gam(
  count ~
    back_o +
    s(months, k = 3) +
    s(months, k = 3, by = back_o) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = reach_tot,
  method = "ML",
  family = negbin(theta)
)
summary(reach_gam)

reach_gam_null <- gam(
  count ~
    # back_o +
    s(months, k = 3) +
    # s(months, k = 3, by = back_o) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = reach_tot,
  method = "ML",
  family = negbin(theta)
)

compareML(reach_gam_null, reach_gam)
```

```{r reach-gam-plot}
plot_smooths(reach_gam, months, facet_terms = back_o, series_length = 25, transform = exp)
```

The following models test time sample.

```{r reach-gam-2}
reach_gam_2 <- gam(
  count ~
    s(months, k = 3) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = reach_tot,
  method = "ML",
  family = negbin(theta)
)
reach_gam_2_null <- gam(
  count ~
    # s(months, k = 3) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = reach_tot,
  method = "ML",
  family = negbin(theta)
)
compareML(reach_gam_2_null, reach_gam_2)
```

```{r reach-gam-2-plot}
plot_smooths(reach_gam_2, months, series_length = 25, transform = exp)
```

## HGs development

The following models test cultural group.

```{r hg-gam}
hg_nb <- glm.nb(count ~ months, data = hg_tot)
theta_2 <- summary(hg_nb)[["theta"]]

hg_gam <- gam(
  count ~
    back_o +
    s(months, k = 3) +
    s(months, k = 3, by = back_o) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = hg_tot,
  method = "ML",
  family = negbin(theta_2)
)
summary(hg_gam)

hg_gam_null <- gam(
  count ~
    # back_o +
    s(months, k = 3) +
    # s(months, k = 3, by = back_o) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = hg_tot,
  method = "ML",
  family = negbin(theta_2)
)

compareML(hg_gam_null, hg_gam)
```

```{r hg-gam-plot}
plot_smooths(hg_gam, months, facet_terms = back_o, series_length = 25, transform = exp)
```

The following models test time sample.

```{r hg-gam-2}
hg_gam_2 <- gam(
  count ~
    s(months, k = 3) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = hg_tot,
  method = "ML",
  family = negbin(theta_2)
)
hg_gam_2_null <- gam(
  count ~
    # s(months, k = 3) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = hg_tot,
  method = "ML",
  family = negbin(theta_2)
)
compareML(hg_gam_2_null, hg_gam_2)
```

```{r hg-gam-2-plot}
plot_smooths(hg_gam_2, months, series_length = 25, transform = exp)
```

## Points development

The following models test cultural group.

```{r point-gam}
point_nb <- glm.nb(count ~ months, data = point_tot)
theta_3 <- summary(point_nb)[["theta"]]

point_gam <- gam(
  count ~
    back_o +
    s(months, k = 3) +
    s(months, k = 3, by = back_o) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = point_tot,
  method = "ML",
  family = negbin(theta_3)
)
summary(point_gam)

point_gam_null <- gam(
  count ~
    # back_o +
    s(months, k = 3) +
    # s(months, k = 3, by = back_o) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = point_tot,
  method = "ML",
  family = negbin(theta_3)
)

compareML(point_gam_null, point_gam)
```

```{r point-gam-plot}
plot_smooths(point_gam, months, facet_terms = back_o, series_length = 25, transform = exp)
```

The following models test time sample.

```{r point-gam-2}
point_gam_2 <- gam(
  count ~
    s(months, k = 3) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = point_tot,
  method = "ML",
  family = negbin(theta_3)
)
point_gam_2_null <- gam(
  count ~
    # s(months, k = 3) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = point_tot,
  method = "ML",
  family = negbin(theta_3)
)
compareML(point_gam_2_null, point_gam_2)
```

```{r point-gam-2-plot}
plot_smooths(point_gam_2, months, series_length = 25, transform = exp)
```

\newpage

# Analysis 1b. Frequency of maternal utterances and contingent talk to infants aged 10-12 months.

For maternal utterances we used a normal distribution, since the distribution of the data was almost normal.
For maternal contingent talks instead we used again the negative binomial distribution for the same reasons as above.

## Maternal utterances development

The following models test cultural group.

```{r utter-gam}
utter_gam <- gam(
  utterances ~
    back_o +
    s(months, k = 3) +
    s(months, k = 3, by = back_o) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = utterances_tot,
  method = "ML"
)
summary(utter_gam)

utter_gam_null <- gam(
  utterances ~
    # back_o +
    s(months, k = 3) +
    # s(months, k = 3, by = back_o) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = utterances_tot,
  method = "ML"
)

compareML(utter_gam_null, utter_gam)
```

```{r utter-gam-plot}
plot_smooths(utter_gam, months, facet_terms = back_o, series_length = 10)
```

The following models test time sample.

```{r utter-gam-2}
utter_gam_2 <- gam(
  utterances ~
    s(months, k = 3) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = utterances_tot,
  method = "ML"
)

utter_gam_2_null <- gam(
  utterances ~
    # s(months, k = 3) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = utterances_tot,
  method = "ML"
)

compareML(utter_gam_2_null, utter_gam_2)
```

## Contingent talks development

The following models test cultural group.

```{r ct-gam}
ct_nb <- glm.nb(ct ~ months, data = all_tot)
theta_4 <- summary(ct_nb)[["theta"]]

ct_gam <- gam(
  ct ~
    back_o +
    s(months, k = 3) +
    s(months, k = 3, by = back_o) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = all_tot,
  method = "ML",
  family = negbin(theta_4)
)
summary(ct_gam)

ct_gam_null <- gam(
  ct ~
    # back_o +
    s(months, k = 3) +
    # s(months, k = 3, by = back_o) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = all_tot,
  method = "ML",
  family = negbin(theta_4)
)

compareML(ct_gam_null, ct_gam)
```

```{r ct-gam-plot}
plot_smooths(ct_gam, months, facet_terms = back_o, series_length = 10, transform = exp)
```

The following models test time sample.

```{r ct-gam-2}
ct_gam_2 <- gam(
  count ~
    s(months, k = 3) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = all_tot,
  method = "ML",
  family = negbin(theta_4)
)

ct_gam_2_null <- gam(
  count ~
    # s(months, k = 3) +
    s(months, dyad, k = 2, bs = "fs", m = 1),
  data = all_tot,
  method = "ML",
  family = negbin(theta_4)
)

compareML(ct_gam_2_null, ct_gam_2)
```

```{r ct-gam-2-plot}
plot_smooths(ct_gam_2, months, series_length = 10, transform = exp)
```

\newpage

# Analysis 1c. Predictors of pointing at 12 months

The following GLMMs test the relation between pointing as the outcome variable and reaches/HoGs.

## Reaches

```{r reach-point-lm}
reach_point_lead_nb <- glm.nb(lead_point ~ reach, data = reach_point_lead)

reach_point_lm <- glmer(
  lead_point ~
    reach *
    background +
    (1|dyad),
  data = reach_point_lead,
  family = negbin(0.2681)
)
summary(reach_point_lm)
```

```{r reach-point-plot}
plot_model(reach_point_lm, type = "pred", terms = c("reach", "background")) + coord_cartesian(ylim = c(0, 20))
```

## HoGs

```{r hg-point-lm}
hg_point_lead_nb <- glm.nb(lead_point ~ ho_gv, data = filter(hg_point_lead, ho_gv < 20))

hg_point_lm <- glmer(
  lead_point ~
    ho_gv *
    background +
    (1|dyad),
  data = filter(hg_point_lead, ho_gv < 20),
  family = negbin(0.2606)
)
summary(hg_point_lm)

hg_point_lm_null <- glmer(
  lead_point ~
    ho_gv +
    background +
    (1|dyad),
  data = filter(hg_point_lead, ho_gv < 20),
  family = negbin(0.2606)
)
anova(hg_point_lm_null, hg_point_lm)
```

```{r hg-point-plot}
plot_model(hg_point_lm, type = "pred", terms = c("ho_gv", "background")) + coord_cartesian(ylim = c(0, 75))
```

\newpage

# Analysis 2. Predictors of vocabulary scores at 12 and 18 months

## Comprehension at 12 and 18 months

### All gestures combined

```{r all-gest-lm}
all_gest_lm <- glm(
  comprehension ~
    count_tot *
    months *
    background,
  data = vocab,
  family = poisson
)
summary(all_gest_lm)
```

```{r all-gest-lm-plot}
plot_model(all_gest_lm, type = "pred", terms = c("count_tot", "months", "background"))
```

### HoGs + points

```{r hgp-lm}
hgp_lm <- glm(
  comprehension ~
    hgp_tot *
    months *
    background,
  data = vocab,
  family = poisson()
)
summary(hgp_lm)
```

```{r hgp-lm-2-plot}
plot_model(hgp_lm, type = "pred", terms = c("hgp_tot", "months", "background"))
```

### Reaches

```{r reach-lm}
reach_lm <- glm(
  comprehension ~
    reach_tot *
    months *
    background,
  data = vocab,
  family = poisson()
)
summary(reach_lm)
```

```{r reach-lm-2-plot}
plot_model(reach_lm, type = "pred", terms = c("reach_tot", "months", "background"))
```

### Maternal utterances

```{r utt-lm}
utt_lm <- glm(
  comprehension ~
    utt_tot *
    months *
    background,
  data = vocab,
  family = poisson()
)
summary(utt_lm)
```

```{r utt-lm-2-plot}
plot_model(utt_lm, type = "pred", terms = c("utt_tot", "months", "background"))
```

### Contingent talks

```{r ct-lm}
ct_lm <- glm(
  comprehension ~
    ct_tot *
    months *
    background,
  data = filter(vocab, ct_tot < 30),
  family = poisson()
)
summary(ct_lm)
```

```{r ct-lm-2-plot}
plot_model(ct_lm, type = "pred", terms = c("ct_tot", "months", "background"))
```

## Production at 12 and 18 months

### All gestures combined

```{r all-gest-lm-2-undsay}
all_gest_prod <- glm(
  production ~
    count_tot *
    months *
    background,
  data = vocab,
  family = poisson()
)
summary(all_gest_prod)
```

```{r all-gest-lm-2-undsay-plot}
plot_model(all_gest_prod, type = "pred", terms = c("count_tot", "months", "background"))
```

### HoGs + point

```{r hgp-lm-2-undsay}
hgp_prod <- glm(
  production ~
    hgp_tot *
    months *
    background,
  data = vocab,
  poisson()
)
summary(hgp_prod)
```

```{r hgp-lm-2-undsay-plot}
plot_model(hgp_prod, type = "pred", terms = c("hgp_tot", "months", "background"))
```

### Reaches

```{r reach-lm-2-undsay}
reach_prod <- glm(
  production ~
    reach_tot *
    months *
    background,
  data = vocab,
  family = poisson()
)
summary(reach_prod)
```

```{r reach-lm-2-undsay-plot}
plot_model(reach_prod, type = "pred", terms = c("reach_tot", "months", "background"))
```

### Maternal utterances

```{r utt-lm-2-undsay}
utt_prod <- glm(
  production ~
    utt_tot *
    months *
    background,
  data = vocab,
  family = poisson()
)
summary(utt_prod)
```

```{r utt-lm-2-undsay-plot}
plot_model(utt_prod, type = "pred", terms = c("utt_tot", "months", "background"))
```

### Contingent talks

```{r ct-lm-2-undsay}
ct_prod <- glm(
  production ~
    ct_tot *
    months *
    background,
  data = filter(vocab, ct_tot < 30),
  family = poisson()
)
summary(ct_prod)
```

```{r ct-lm-2-undsay-plot}
plot_model(ct_prod, type = "pred", terms = c("ct_tot", "months", "background"))
```

\newpage

# R session

```{r session}
sessionInfo()
```

