---
title: "Infant gestures"
author: "Stefano Coretta"
date: "17/07/2018"
output: 
  pdf_document: 
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = normalizePath("../"))
library(fitdistrplus)
library(tidyverse)
theme_set(theme_minimal())
```

# Read data

```{r read, message=FALSE}
gestures <- read_csv("./data/gestures.csv")

gestures_tot <- gestures %>%
  group_by(dyad, background, months, gesture) %>%
  summarise(
    count = sum(count),
    ct = sum(ct)
  ) %>%
  ungroup() %>%
  mutate(
    gesture = factor(gesture, levels = c("reach", "point", "ho_gv"))
  ) %>%
  mutate_if(is.character, as.factor)

utterances <- read_csv("./data/utterances.csv")

# NAs not removed in sum()
utterances_tot <- utterances %>%
  group_by(dyad, background, months) %>%
  summarise(
    utterances = sum(utterances)
  ) %>%
  ungroup() %>%
  mutate_if(is.character, as.factor)

point <- gestures %>%
  filter(gesture == "point") %>%
  group_by(dyad, background, months) %>%
  summarise(
    count = sum(count)
  ) %>%
  ungroup() %>%
  mutate_if(is.character, as.factor)

utter_point <- left_join(utterances_tot, point) %>%
  rename(point = count)

utterances_compl <- utterances %>% na.omit()
utterances_tcompl <- utterances_tot %>% na.omit()

hgp_tot <- gestures_tot %>%
  filter(gesture != "reach") %>%
  group_by(dyad, background) %>%
  summarise(hgp_tot = sum(count))

vocab_gest <- gestures_tot %>%
  group_by(dyad, background) %>%
  summarise(count_tot = sum(count), ct_tot = sum(ct)) %>%
  full_join(y = hgp_tot)

vocab_utt <- utterances_tot %>%
  group_by(dyad, background) %>%
  summarise(utt_tot = sum(utterances))

vocab <- read_csv("./data/vocab.csv") %>%
  full_join(y = vocab_gest) %>%
  full_join(y = vocab_utt) %>%
  arrange(dyad, months) %>%
  mutate_if(is.character, as.factor)
```

# Summaries

Number of dyads per background.

```{r n-dyads}
gestures %>% group_by(background) %>% summarise(n = n_distinct(dyad))
```

```{r n-dyads}
utterances %>% group_by(background) %>% summarise(n = n_distinct(dyad))
```

20 Bangladeshi, 20 Chinese, 19 English.

`gestures` has 21 missing values. `utterances` has 12 missing values.

```{r}
gestures_tot %>%
  dplyr::select(-dyad, -months) %>%
  group_by(gesture, background) %>%
  summarise_all(mean, na.rm = TRUE)
```


# Plot data

## Gestures

```{r density}
gestures_tot %>%
  ggplot(aes(count)) +
  geom_density() +
  geom_rug() +
  geom_vline(xintercept = median(gestures_tot$count, na.rm = TRUE), linetype = "dashed", colour = "orange") +
  geom_vline(xintercept = mean(gestures_tot$count, na.rm = TRUE), linetype = "dotted", colour = "blue")
```

```{r density-31}
gestures_tot %>%
  filter(count < 31) %>%
  ggplot(aes(count)) +
  geom_density() +
  geom_rug() +
  geom_vline(xintercept = median(gestures_tot$count, na.rm = TRUE), linetype = "dashed", colour = "orange") +
  geom_vline(xintercept = mean(gestures_tot$count, na.rm = TRUE), linetype = "dotted", colour = "blue")
```

```{r descdist}
gest_na <- na.omit(gestures_tot)
descdist(gest_na$count, discrete = TRUE)
```

```{r pois-plot}
plot(fitdist(gest_na$count, "pois"))
```

```{r nbinom-plot}
plot(fitdist(gest_na$count, "nbinom"))
```

```{r density-months-gest}
gestures_tot %>%
  ggplot(aes(count, fill = as.factor(months))) +
  geom_density(alpha = 0.5) +
  facet_grid(~ gesture)
```

```{r background-jitter}
gestures_tot %>%
  ggplot(aes(as.factor(background), count, colour = background)) +
  geom_jitter(width = 0.2, alpha = 0.5) +
  stat_summary(fun.y = median, geom = "point", shape = 18, size = 4, color = "black") +
  scale_color_brewer(type = "qual", palette = "Dark2")
```

```{r gest-background-jitter}
gestures_tot %>%
  ggplot(aes(as.factor(background), count, colour = background)) +
  geom_jitter() +
  stat_summary(fun.y = median, geom = "point", shape = 18, size = 4, color = "black") +
  scale_color_brewer(type = "qual", palette = "Dark2") +
  facet_grid(cols = vars(gesture))
```

```{r gest-months-jitter}
gestures_tot %>%
  ggplot(aes(as.factor(months), count)) +
  geom_jitter() +
  stat_summary(fun.y = median, geom = "point", shape = 18, size = 4, color = "red") +
  facet_grid(cols = vars(gesture))
```

```{r gest-back-month-jitter}
gestures_tot %>%
  ggplot(aes(as.factor(months), count)) +
  geom_jitter(alpha = 0.5, width = 0.15) +
  stat_summary(fun.y = median, geom = "point", shape = 18, size = 2, color = "red") +
  facet_grid(vars(background), vars(gesture))
```

```{r gest-background-jitter-2}
gestures_tot %>%
  ggplot(aes(as.factor(months), count)) +
  geom_jitter(width = 0.15) +
  stat_summary(fun.y = median, geom = "point", shape = 18, size = 4, color = "red") +
  facet_wrap(vars(background, gesture), scales = "free")
```

```{r gest-connect}
gestures_tot %>%
  ggplot(aes(as.factor(months), count, colour = background)) +
  geom_point(alpha = 0.5) +
  geom_line(aes(group = dyad)) +
  facet_grid(vars(background), vars(gesture))
```

```{r gest-connect-ba}
gestures_tot %>%
  filter(background == "Bangladeshi") %>%
  ggplot(aes(as.factor(months), count, colour = dyad)) +
  geom_point(alpha = 0.5) +
  geom_line(aes(group = dyad)) +
  facet_grid(cols = vars(gesture)) +
  theme(legend.position = "none")
```

```{r gest-connect-ch}
gestures_tot %>%
  filter(background == "Chinese") %>%
  ggplot(aes(as.factor(months), count, colour = dyad)) +
  geom_point(alpha = 0.5) +
  geom_line(aes(group = dyad)) +
  facet_grid(cols = vars(gesture)) +
  theme(legend.position = "none")
```

```{r gest-connect-en}
gestures_tot %>%
  filter(background == "English") %>%
  ggplot(aes(as.factor(months), count, colour = dyad)) +
  geom_point(alpha = 0.5) +
  geom_line(aes(group = dyad)) +
  facet_grid(cols = vars(gesture)) +
  theme(legend.position = "none")
```

## Utterances

```{r utter-density}
utterances %>%
  ggplot(aes(utterances)) +
  geom_density() +
  geom_rug()
```

```{r utter-tot-density}
utterances_tot %>%
  ggplot(aes(utterances)) +
  geom_density() +
  geom_rug()
```

```{r utter-tot-distr}
descdist(utterances_tcompl$utterances, discrete = TRUE)
```


```{r norm-plot}
plot(fitdist(utterances_tcompl$utterances, "norm"))
```

```{r utter-background}
utterances_tot %>%
  ggplot(aes(utterances, fill = background)) +
  geom_density(alpha = 0.5, colour = NA) +
  geom_rug()
```

```{r utter-months}
utterances_tot %>%
  ggplot(aes(utterances, fill = as.factor(months))) +
  geom_density(alpha = 0.5, colour = NA) +
  geom_rug()
```

```{r utter-months-jitter}
utterances_tot %>%
  ggplot(aes(as.factor(months), utterances)) +
  geom_jitter(width = 0.1)
```

```{r utter-months-jitter}
utterances_tot %>%
  ggplot(aes(as.factor(months), utterances, colour = background)) +
  geom_jitter(width = 0.1) +
  facet_grid(~ background)
```

```{r utter-months-line}
utterances_tot %>%
  group_by(background, months) %>%
  summarise(mean = mean(utterances, na.rm = TRUE)) %>%
  ggplot(aes(as.factor(months), mean, group = background, colour = background)) +
  geom_point() +
  geom_line() +
  ylim(c(min(utterances_tot$utterances, na.rm = TRUE), max(utterances_tot$utterances, na.rm = TRUE)))
```

```{r utter-months-line}
utterances_tot %>%
  group_by(background, months) %>%
  summarise(median = median(utterances, na.rm = TRUE)) %>%
  ggplot(aes(as.factor(months), median, group = background, colour = background)) +
  geom_point() +
  geom_line() +
  ylim(c(min(utterances_tot$utterances, na.rm = TRUE), max(utterances_tot$utterances, na.rm = TRUE)))
```

```{r utter-months-jitter}
utterances %>%
  ggplot(aes(as.factor(months), utterances, colour = task)) +
  geom_jitter(width = 0.1) +
  facet_grid(~ task)
```



```{r utter-months-background-jitter}
utterances %>%
  ggplot(aes(as.factor(months), utterances, colour = task)) +
  geom_jitter(width = 0.1) +
  facet_grid(background ~ task)
```

```{r utter-months-background-jitter}
utterances %>%
  ggplot(aes(as.factor(months), utterances, colour = task, group = dyad)) +
  geom_point() +
  geom_line() +
  facet_grid(background ~ task)
```

```{r utter-months-background-jitter-2}
utterances_tot %>%
  ggplot(aes(as.factor(months), utterances, colour = background)) +
  geom_jitter(width = 0.1) +
  facet_grid(background ~ .)
```

```{r utter-months-background-line}
utterances_tot %>%
  ggplot(aes(as.factor(months), utterances, colour = background)) +
  # geom_boxplot(width = 0.5, aes(colour = NULL)) +
  geom_point() +
  geom_line(aes(group = dyad)) +
  facet_grid(background ~ .)
```

```{r utter-background-jitter}
utterances_tot %>%
  ggplot(aes(background, utterances, colour = background)) +
  geom_jitter(width = 0.2) +
  stat_summary(fun.y = median, geom = "point", shape = 18, size = 6, color = "black")
```

## Utterances and points

```{r utter-point}
utter_point %>%
  ggplot(aes(utterances, point)) +
  geom_point() +
  geom_smooth(method = "lm")
```

```{r utter-point}
utter_point %>%
  ggplot(aes(utterances, point, colour = as.factor(months))) +
  geom_point() +
  geom_smooth(method = "lm")
```

```{r utter-point-months}
utter_point %>%
  ggplot(aes(utterances, point, colour = as.factor(months))) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(~ background)
```

```{r point-lead}
utter_point_lead <- utter_point %>%
  group_by(dyad) %>%
  mutate(
    lead_point = lead(point)
  ) %>%
  filter(months != 12)
```

```{r point-lead-plot}
utter_point_lead %>%
  ggplot(aes(utterances, lead_point)) +
  geom_point() +
  geom_smooth(method = "lm")
```

```{r point-lead-back}
utter_point_lead %>%
  ggplot(aes(utterances, lead_point, colour = background)) +
  geom_point() +
  geom_smooth(method = "lm")
```

## Points and hold out and gives

```{r point-hg}
point_hg <- gestures_tot %>%
  dplyr::select(-ct) %>%
  spread(gesture, count) %>%
  dplyr::select(-reach) %>%
  group_by(dyad) %>%
  mutate(
    lead_hg = lead(ho_gv)
  ) %>%
  filter(months != 12)
```

```{r point-hg-line}
point_hg %>%
  ggplot(aes(point, lead_hg)) +
  geom_point() +
  geom_smooth(method = "lm")
```

```{r filtered}
point_hg %>%
  filter(point < 20) %>%
  ggplot(aes(point, lead_hg)) +
  geom_point() +
  geom_smooth(method = "lm")
```

```{r line-background}
point_hg %>%
  filter(point < 20) %>%
  ggplot(aes(point, lead_hg, colour = background)) +
  geom_point() +
  geom_smooth(method = "lm")
```

```{r hg-point-lead}
hg_point_lead <- gestures_tot %>%
  dplyr::select(-ct) %>%
  spread(gesture, count) %>%
  dplyr::select(-reach) %>%
  group_by(dyad) %>%
  mutate(
    lead_point = lead(point)
  ) %>%
  filter(months != 12)
```

```{r}
hg_point_lead %>%
  ggplot(aes(ho_gv, lead_point)) +
  geom_point() +
  geom_smooth(method = "lm")
```

```{r}
hg_point_lead %>%
  ggplot(aes(ho_gv, lead_point, colour = background)) +
  geom_point() +
  geom_smooth(method = "lm")
```

```{r}
hg_point_lead %>%
  filter(ho_gv < 20) %>%
  ggplot(aes(ho_gv, lead_point, colour = background)) +
  geom_point() +
  geom_smooth(method = "lm")
```

## Mother's contingent talks

```{r ct-density}
gestures_tot %>%
  ggplot(aes(ct)) +
  geom_density()
```

Not many contingent talks.

```{r ct-gest-density}
gestures_tot %>%
  ggplot(aes(ct, fill = gesture)) +
  geom_density(alpha = 0.5)
```

```{r t-hist}
gestures_tot %>%
  ggplot(aes(ct, fill = gesture)) +
  geom_histogram() +
  facet_grid(~ gesture)
```

```{r ct-hist-2}
gestures_tot %>%
  ggplot(aes(ct, fill = gesture)) +
  geom_histogram() +
  facet_grid(background ~ gesture)
```

```{r ct-jitt}
gestures_tot %>%
  ggplot(aes(as.factor(months), ct)) +
  geom_jitter(width = 0.2, alpha = 0.3)
```

There is a big outlier and it is e05, which is also the super pointer, if I am not mistaken.

```{r ct-jitt-med}
gestures_tot %>%
  filter(ct < 20) %>%
  ggplot(aes(as.factor(months), ct)) +
  geom_jitter(width = 0.2, alpha = 0.3) +
  stat_summary(fun.y = median, geom = "point", shape = 18, size = 5, color = "red")
```

```{r ct-jitt-mean}
gestures_tot %>%
  filter(ct < 20) %>%
  ggplot(aes(as.factor(months), ct)) +
  geom_jitter(width = 0.2, alpha = 0.3) +
  stat_summary(fun.y = mean, geom = "point", shape = 18, size = 5, color = "red")
```

It looks like there is an increase over visit time, but mean shows it (not median, not surprising since there are a lot of 0 CTs).

```{r ct-connect}
gestures_tot %>%
  filter(ct < 20) %>%
  ggplot(aes(as.factor(months), ct, group = dyad, colour = gesture)) +
  geom_point() +
  geom_line(alpha = 0.2) +
  facet_grid(gesture ~ .) +
  scale_color_brewer(type = "qual", palette = "Dark2")
```

But indeed there are a few mothers that show an increase.

```{r ct-connect-background}
gestures_tot %>%
  filter(ct < 20) %>%
  ggplot(aes(as.factor(months), ct, group = dyad, colour = background)) +
  geom_point() +
  geom_line(alpha = 0.2) +
  facet_grid(background ~ gesture) +
  scale_color_brewer(type = "qual", palette = "Dark2")
```

The mothers with increasing CTs are mostly Chinese and English.

```{r ct-point-lead}
ct_point_lead <- gestures_tot %>%
  filter(gesture == "point") %>%
  select(-gesture) %>%
  rename(point = count) %>%
  group_by(dyad) %>%
  mutate(
    lead_point = lead(point)
  ) %>%
  filter(months != 12)
```

```{r ct-point-lead}
ct_point_lead %>%
  ggplot(aes(ct, lead_point)) +
  geom_point() +
  geom_smooth(method = "lm")
```

```{r ct-point-lead-regression}
ct_point_lead %>%
  filter(ct < 20) %>%
  ggplot(aes(ct, lead_point)) +
  geom_point() +
  geom_smooth(method = "lm")
```

```{r ct-point-lead-regression-background}
ct_point_lead %>%
  filter(ct < 20) %>%
  ggplot(aes(ct, lead_point, colour = background)) +
  geom_point() +
  geom_smooth(method = "lm")
```

# Vocab scores

```{r}
vocab %>%
  ggplot(aes(understand, fill = background)) +
  geom_density(alpha = 0.5)
```

```{r}
vocab %>%
  ggplot(aes(background, understand)) +
  geom_boxplot()
```

## Gesture count total

```{r}
vocab %>%
  ggplot(aes(count_tot, understand, colour = background)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(~ months)
```

```{r}
vocab %>%
  ggplot(aes(count_tot, understand)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(~ months) +
  xlim(0, 150)
```

```{r}
vocab %>%
  ggplot(aes(count_tot, und_say, colour = background)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(~ months)
```

## Hold out and gives and points

```{r}
vocab %>%
  ggplot(aes(hgp_tot, understand, colour = background)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(~ months)
```

```{r}
vocab %>%
  ggplot(aes(hgp_tot, understand)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(~ months)
```

```{r}
vocab %>%
  filter(hgp_tot < 120) %>%
  ggplot(aes(hgp_tot, understand, colour = background)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(~ months)
```

```{r}
vocab %>%
  ggplot(aes(hgp_tot, und_say, colour = background)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(~ months)
```

## Contingent talks

```{r}
vocab %>%
  ggplot(aes(ct_tot, understand)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(~ months)
```

```{r}
vocab %>%
  filter(ct_tot < 75) %>%
  ggplot(aes(ct_tot, understand)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(~ months)
```

```{r}
vocab %>%
  filter(ct_tot < 75) %>%
  ggplot(aes(ct_tot, understand, colour = background)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(~ months)
```

```{r}
vocab %>%
  # filter(ct_tot < 75) %>%
  ggplot(aes(ct_tot, und_say)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(~ months)
```

```{r}
vocab %>%
  filter(ct_tot < 25) %>%
  ggplot(aes(ct_tot, und_say)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(~ months)
```

```{r}
vocab %>%
  filter(ct_tot < 25) %>%
  ggplot(aes(ct_tot, und_say, colour = background)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(~ months)
```

## Mother utterances

```{r}
vocab %>%
  ggplot(aes(utt_tot, understand)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(~ months)
```

```{r}
vocab %>%
  ggplot(aes(utt_tot, understand, colour = background)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(~ months)
```

```{r}
vocab %>%
  ggplot(aes(utt_tot, und_say)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(~ months)
```

```{r}
vocab %>%
  ggplot(aes(utt_tot, und_say, colour = background)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(~ months)
```
